Combined Task and Motion Planner through an Interface Layer

### 2015-04-17 documentation/draft.tex
backtracking worlds

Bianca will finish writing this section and the corresponding subsections tomorrow

@@

NOTE TO BIANCA: include paragraph about how our version differs from the paper's version as a speedup

@@

>>>>

@@

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.

@@

\section{Benchmarking}

\subsection{Testing}

\subsection{Procedure}

\subsection{Results}

to include:

-tables of results

-description of how we did benchmarking

-in particular, description of why we did number of calls to task and motion planner instead of total time taken

-discussion of testing procedure as well
